Approaching causal linkages between SES structures and outcomes of the Yellow River Basin, China

### 2022-11-04 docs/papers/01_manuscript/04_discussion.tex
docs(manuscript.tex,-introduction,-discussion): change title, emphasize methology

\label{discussion-3}
On the other hand, social-ecological matches can also be supported by structural effects.
After 98-UBR, the YRCC could adjust surface water use quotas according to climate conditions for the whole YRB.
When the YRCC began to coordinate among stakeholders, the external appeals of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)
\cite{krieger1955, ostrom1990}.
During this period, proportional decreased water use of provinces indicated expected river regulating results (see \nameref{result-3}).
Meanwhile, our model also demonstrates that in this case, the unified scale-matched institution was indispensable for decreased water use.
However, since the 98-UBR only regulated surface water use, many clues suggested the institution shift may cause broader influences (cascading effects) because of unsatisfied water demands. 
For example, literature estimated increased groundwater withdrawals after 98-UBR in many intensive irrigation regions, despite little eligible data on groundwater use and stakeholders being accessible \cite{sun2022b}.
Since the 21st century, similar water quota policies started to be implemented nationally and altering the relationship between social actors and resource units. 
As both of the institutional shifts examined here induced unexpected changes or cascading effects within SESs, better governance is calling for more institutional analysis of coupled human and natural systems in the future.

>>>>

\label{discussion-3}
On the other hand, social-ecological matches can also be supported by structural effects.
After 98-UBR, the YRCC could adjust surface water use quotas according to climate conditions for the whole YRB.
When the YRCC began to coordinate among stakeholders, the external appeals of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)
\cite{krieger1955, ostrom1990}.
During this period, proportional decreased water use of provinces indicated expected river regulating results (see \nameref{result-3}).
Meanwhile, our model also demonstrates that in this case, the unified scale-matched institution was indispensable for decreased water use.
However, since the 98-UBR only regulated surface water use, many clues suggested the institution shift may cause broader influences (cascading effects) because of unsatisfied water demands.
For example, literature estimated increased groundwater withdrawals after 98-UBR in many intensive irrigation regions, despite little eligible data on groundwater use and stakeholders being accessible \cite{sun2022b}.
Since the 21st century, similar water quota policies started to be implemented nationally and altering the relationship between social actors and resource units.
As both institutional shifts examined here induced unexpected changes or cascading effects within SESs, better governance calls for more institutional analysis of coupled human and natural systems in the future.

### 2022-11-04 docs/papers/01_manuscript/manuscript.tex
tem
docs(manuscript.tex,-introduction,-discussion): change title, emphasize methology

\documentclass[default, sn-standardnature]{sn-jnl}
\usepackage{amsmath,graphicx,array}
\usepackage{dcolumn,soul}%
\let\openbox\relax
\usepackage{amsthm}
\usepackage[figuresright]{rotating}%
\usepackage{algorithm, algorithmicx, algpseudocode}
\usepackage{listings}%
\usepackage{hyperref}
\newgeometry{left=2cm, right=2cm}
\linespread{1.5}
% \usepackage[nofiglist,notablist]{endfloat}
\makeatletter
\def\uns{\ifmmode\,\else$\,$\fi}%
\newtheorem{defn}{Definition}
\newtheorem{thm}{Theorem}
\newtheorem{ass}{Assumption}
\newtheorem{prop}{Proposition}
\newtheorem{fig}{Fig.}
\newtheorem{case}{Case}
\newtheorem{case_appendix}{Case}
\newtheorem{example}{Example}[section]
\renewcommand{\proofname}{\textbf{Proof}}
\newtheorem{property}{Property}
\newtheorem{remark}{Remark}
%\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{float}
\usepackage{multirow}
\usepackage{lineno}
\setenumerate{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=0pt}
\setitemize{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=5pt}
\setdescription{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=5pt}

@@

\bibliographystyle{../nsr}

\title{Approaching social-ecological matches of river basin systems for sustainability}  %! Notice Input

@@

% \authornote{\textbf{Corresponding authors.} Email: shuaiwang@bnu.edu.cn}
%\authornote{Shuang Song and Huiyu Wen equally contributed to this work.}
\renewcommand\linenumberfont{\normalfont\bfseries\small}
\linenumbers
\abstract{
     Increasing competition for water is leading to depletion of freshwater globally and calls for efficient institutions in water governance.
     Alignments of social-ecological system (SES) structures are a crucial approach to institutional matches, but an understanding of its causal links and underlying processes are still weaknesses.
     To fill these knowledge gaps, we select the Yellow River Basin (YRB) in China as a typical case study to quantitatively measure the effects of SES structures changing because it is one of the most anthropogenically altered large river basins.
     Under different water allocation institutions, its streamflow was first overdrawn, then dried up, and finally has been successfully restored.
     We focused on two institutional shifts, the Water Allocation Scheme that began in 1987 (87-WAS) and the Unified Basinal Regulation that took over in 1998 (98-UBR), which re-framed different SES structures.
     We conduct counterfactual identification on the effect of these institutional shifts, our results suggested that during the decade following the introduction of the 87-WAS, observed water use of the YRB increased by $8.57\%$ more than expected, while 98-UBR ultimately decreased total water use.
     Furthermore, these heterogeneous effects of water use responses to SES structures aligned with our further theoretical marginal benefits analysis, supporting the hypothesis that SES structural changes played a vital role in sustainable water use.
     This quasi-natural experiment on the YRB offers profound insights into the links between SESs structures and outcomes, suggesting that fragmented ecological units linked to separated social actors should be avoided for sustainability.
     }  %! Notice input

\keywords{Yellow River, water use, water governance, social-ecological system, institutional fit}  %! Notice input
\maketitle

>>>>

\documentclass[default, sn-standardnature]{sn-jnl}
\usepackage{amsmath, graphicx, array}
\usepackage{dcolumn, soul}%
\let\openbox\relax
\usepackage{amsthm}
\usepackage[figuresright]{rotating}%
\usepackage{algorithm, algorithmicx, algpseudocode}
\usepackage{listings}%
\usepackage{hyperref}
\newgeometry{left=2cm, right=2cm}
\linespread{1.5}
% \usepackage[nofiglist,notablist]{endfloat}
\makeatletter
\def\uns{\ifmmode\,\else$\,$\fi}%
\newtheorem{defn}{Definition}
\newtheorem{thm}{Theorem}
\newtheorem{ass}{Assumption}
\newtheorem{prop}{Proposition}
\newtheorem{fig}{Fig.}
\newtheorem{case}{Case}
\newtheorem{case_appendix}{Case}
\newtheorem{example}{Example}[section]
\renewcommand{\proofname}{\textbf{Proof}}
\newtheorem{property}{Property}
\newtheorem{remark}{Remark}
%\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{float}
\usepackage{multirow}
\usepackage{lineno}
\setenumerate{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=0pt}
\setitemize{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=5pt}
\setdescription{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=5pt}

@@

% \bibliographystyle{../nsr}

\title{Approaching causal linkages between SES structures and outcomes of the Yellow River Basin, China}  %! Notice Input

@@

% \authornote{\textbf{Corresponding authors.} Email: shuaiwang@bnu.edu.cn}
%\authornote{Shuang Song and Huiyu Wen equally contributed to this work.}
\renewcommand\linenumberfont{\normalfont\bfseries\small}
\linenumbers
\abstract{
     Increasing competition for water is leading to depletion of freshwater globally and calls for efficient institutions in water governance.
     Alignments of social-ecological system (SES) structures are a crucial approach to institutional matches, but an understanding of its causal links and underlying processes are still weaknesses.
     To fill these knowledge gaps, we select the Yellow River Basin (YRB) in China as a typical case study to quantitatively measure the effects of SES structures changing because it is one of the most anthropogenically altered large river basins.
     Under different surface water allocation institutions, its streamflow was first overdrawn, then dried up, and finally has been successfully restored.
     We focused on two institutional shifts, the Water Allocation Scheme that began in 1987 (87-WAS) and the Unified Basinal Regulation that took over in 1998 (98-UBR), which re-framed different SES structures.
     We conduct counterfactual identification on the effect of these institutional shifts, our results suggested that during the decade following the introduction of the 87-WAS, observed water use of the YRB increased by $8.57\%$ more than expected, while 98-UBR ultimately decreased total water use.
     Furthermore, these heterogeneous effects of water use responses to SES structures aligned with our further theoretical marginal benefits analysis, supporting the hypothesis that SES structural changes played a vital role.
     This quasi-natural experiment on the YRB offers profound insights into the links between SESs structures and outcomes, suggesting that fragmented ecological units linked to separated social actors should be avoided for sustainability.
     }  %! Notice input

\keywords{water use, water governance, social-ecological system, institutional fit, Yellow River}  %! Notice input
\maketitle
